---
title: "10-data-cleaning"
output: html_notebook
---
# Introduction
We investigate the variables that are important to our project.

## import package
```{r}
library(scales)
library(forcats)
library(dplyr)
library(ggpubr)
library(tidyverse)
library(readr)
library(janitor)
library(lubridate)
library(nnet)
library(assertr)
library(tidyverse)
library(tidytext)
library(textdata)
library(data.table)
library(ggthemes)
library(scales)
library(forcats)
library(dplyr)
library(ggpubr)
```

## import data
```{r}
apps_game <- read_csv("appstore_games.csv") %>% clean_names()
games <- apps_game
```

## Data cleaning


### Drop useless or biased data

1. Games without User Rating or rating count should be dropped.
```{r}
games <- games %>% filter(!is.na(user_rating_count)) %>% filter(!is.na(average_user_rating))
```

2. Drop useless variables for our project including 'url' and 'icon_url'
```{r}
games <- games %>% 
  select(everything(),-url,-icon_url)
```


Top 10% 

```{r}
games %>% 
  arrange(-user_rating_count) %>% 
  slice(1: (0.11 * nrow(games))) %>% 
  arrange(user_rating_count)
```




### fill NA values
We don't need to fill the NA value in subtitle, in_app_purchases, languages rigt now.

For price, we should replace NA by 0
```{r}
games[is.na(games$price),"price"] <- 0
```


## Data minipulation

### age into numeric format
```{r}
age <- as.numeric(str_extract(games$age_rating,"[0-9]*"))

games <- data.frame(games, age)

games <- games %>% 
  select(everything(), -age_rating)

```

### processing language
```{r}
language <- str_split(games$languages,", ")
unique(unlist(language))
## Since there are so many languages, only choose the most frequently used language as dummy variables

languages <- na.omit(data.frame(unlist(language)))
languages %>% 
  group_by(unlist.language.) %>% 
  summarise(count = n()) %>%
  arrange(-count) # I will only pick top 10 frequently used language because there is a sharp decrease after top 10
```

Change it into dummy varibles 
```{r}
language_top <- c("EN","ZH","DE","FR","ES","JA","RU","IT","PT","KO") # create language list

language_dummy <- as.data.frame(matrix(NA, nrow = nrow(games), ncol = 10))

names(language_dummy) <- language_top

for (j in seq_along(language)){
  for (i in seq_along(language_top)){
    if (language_top[i] %in% language[[j]]){
      language_dummy[j,i] = 1
    }
    else language_dummy[j,i] = 0
  }
}
# Now we successfully get dummy variables for language
```

### change the data into lubridate version that could be easier to use
```{r}
games <- games %>% 
  mutate(original_release_date = dmy(original_release_date),
         current_version_release_date = dmy(current_version_release_date))

# get the release year
games <- games %>% 
  mutate(release_year = year(original_release_date))

# current_version_release_date

```

### processing in game purchase
```{r}
in_app_p <- str_split(games$in_app_purchases,", ")
unique(unlist(in_app_p))
# So many values

# We could create a column to determine whether it has in app purchase or not
games <- games %>% 
  mutate(in_app_purchasing = if_else(is.na(in_app_purchases), 0,1)
  )
```

### Re-determine the primary specific genre of the game

Since all the games belong to strategic games, we don't think 'Strategy' or 'Games ' should be the specific main genre of one game. 

After we look at the 'primary_genre' and 'genres' columns, we may determin the first word except for 'Games' and 'Strategy' as the primary specific genre of the game.

However, if the game only contains "Games" and "Strategy", we should determine it as 'pure' strategy game.

```{r}
genre_list <- str_split(games$genres,", ")

specific_primary_genre <- rep(NA, length = nrow(games))

for (i in seq_along(genre_list)){
  if (length(genre_list[[i]]) == 2 & 
      genre_list[[i]][[1]] %in% c("Games","Strategy") & 
      genre_list[[i]][[2]] %in% c("Games","Strategy")){
    specific_primary_genre[i] = "Strategy"
  }
  else if (genre_list[[i]][[1]] %in% c("Games","Strategy") & genre_list[[i]][[2]] %in% c("Games","Strategy")){
    specific_primary_genre[i] = genre_list[[i]][[3]]
  }
  else if (genre_list[[i]][[1]] %in% c("Games","Strategy")) {
    specific_primary_genre[i] = genre_list[[i]][[2]]
  }
  else {specific_primary_genre[i] = genre_list[[i]][[1]]}
}

games <- data.frame(games, specific_primary_genre)
```

size to size_MB

```{r}
games <- games %>%
  mutate(size_MB = size/ 10^6)
```




the density of the number of ratings

```{r}
games %>% 
  ggplot(aes(x = log10(user_rating_count)))+
  geom_density(kernel = "epanechnikov",adjust = 0.5)+
  theme_classic()+
  scale_y_continuous(name = "Density")+
  scale_x_continuous(breaks = seq(0,6,1),name = "The number of ratings (in log10 scales)")

```

```{r}
games %>% 
  ggplot(aes(x = log10(user_rating_count), y = size_MB))+
  geom_point()+
  theme()+
  scale_x_continuous(breaks = seq(0,6,1),name = "The number of ratings (in log10 scales)")+
  scale_y_continuous(name = "size (MB)") +
  theme_classic()
```


