---
title: "20-Initial-Exploration"
output: html_notebook
---


# Size

```{r grouping the sizes}
games <- games %>%
  mutate(size_MB = size/ 10^6) %>%
  mutate(size_group = case_when(size_MB < 10 ~ "< 10MB",
                                size_MB < 100 ~ "10-100MB",
                                size_MB < 200 ~ "100-200MB",
                                size_MB < 500 ~ "200-500MB",
                                size_MB < 1000 ~ "500-1000MB",
                                TRUE ~ "> 1000MB")) %>%
  mutate(size_group = factor(size_group, levels = c("< 10MB","10-100MB","100-200MB","200-500MB","500-1000MB","> 1000MB")))
```

```{r graph of the game sizes of the Top 10% games, eval = F}
size_intervals_top_10 <- games %>% 
  arrange(-user_rating_count) %>% 
  slice(1: (0.1 * nrow(games)))%>%
  group_by(size_group) %>% 
  summarise(n = n())

size_intervals_top_10

ggplot(size_intervals_top_10, aes(x=size_group, y = n))+
  geom_col(fill = "blue", alpha = 0.5)+
  xlab("game size")+
  ylab("Top 10%")+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r size distributions of games in 2018 and 2019}
all_size <- games %>% filter(release_year == 2018 | release_year == 2019) %>% 
  mutate(group = case_when(release_year == 2018 ~ "all_2018",
                           release_year == 2019 ~ "all_2019"))

games %>% 
  arrange(-user_rating_count) %>% 
  slice(1: (0.1 * nrow(games)))%>%
  filter(release_year == 2018 | release_year == 2019) %>% 
  mutate(group = case_when(release_year == 2018 ~ "top_2018",
                           release_year == 2019 ~ "top_2019")) %>% 
  bind_rows(all_size) %>% 
  ggplot(aes(x = group, y = size_MB, color = group))+
  geom_boxplot()+
  scale_y_continuous(name = "Size (MB)", limits = c(0,500))+
  scale_x_discrete(name = " ", labels = c("All games in 2018", "All games in 2019", "Top games in 2018", "Top games in 2019"))+
  theme_classic()+
  scale_color_manual(values = c("#F8766D","#F8766D","#00BFC4","#00BFC4"))+
  guides(color=FALSE)
```



# Age

### Age versus number of User Ratings
```{r Age Versus User rating count}
unique(games$age)
games %>% arrange(-user_rating_count) %>%
  mutate(group = "all") %>%
  bind_rows(games %>%
  arrange(-user_rating_count) %>%
  slice(1: (0.1 * nrow(games)))%>%
  mutate(group = "top")) %>%
  group_by(age, group) %>%
  summarise(count = n()) %>%
  mutate(share = case_when(group == "all" ~ (count / 7561),
                           group == "top" ~ (count/756))) %>%
  ggplot(aes(x = as.factor(age), y = share, group = group, color = group, fill = group))+
  geom_bar(stat = 'identity', position = 'dodge')+
  theme_classic()+
  scale_y_continuous(name = "Proportion")+
  scale_x_discrete(labels = c("4+","9+","12+","17+"), name = "Content rating")+
  scale_fill_manual(name = "", labels = c("All","Top"),values = c("#EFC000FF","#0073C2FF"))+
  scale_color_manual(name = "", labels = c("All","Top"),values = c("#EFC000FF","#0073C2FF"))+
  theme(legend.position = "top")
```


```{r Age Versus User rating count, in yearly trend}
games %>%
  arrange(-user_rating_count) %>%
  slice(1: (0.1 * nrow(games))) %>%
  group_by(release_year,age) %>%
  summarise(count = n()) %>%
  filter(release_year != 2019) %>%
  ggplot(aes(x = as.factor(release_year), y = count, group = as.factor(age), color = as.factor(age)))+
  geom_line(aes(color = as.factor(age), size = as.factor(age),linetype = as.factor(age)))+
  scale_linetype_manual(values=c("longdash", "longdash","solid","dashed"),name = "", labels = c("4+","9+","12+","17+"))+
  scale_color_manual(values=c("lightblue3", "goldenrod2","#F8766D","grey65"),name = "", labels = c("4+","9+","12+","17+"))+
  scale_size_manual(values=c(1,1,1.12,0.9),name = "", labels = c("4+","9+","12+","17+"))+
  scale_x_discrete(name = "Release year")+
  scale_y_continuous(name = "The number of games")+
  theme_classic()
```


# Language
```{r how does "multiple languages" affect size}
games_sizes_language <- apps_game %>%
  mutate(size_MB = size/ 10^6) %>%
  select(languages, size_MB) 

ggplot(games_sizes_language, aes(x = languages, y = size_MB)) +
  geom_count(alpha = 0.5, fill = "yellow")
```

```{r}
games_l <- data.frame(games, language_dummy)

l1 <- games_l %>% 
  arrange(-user_rating_count) %>% 
  slice(1: (0.1 * nrow(games)))%>%
  summarise(English = mean(EN),
            Chinese = mean(ZH),
            German = mean(DE),
            French = mean(FR),
            Spanish = mean(ES),
            Japanese = mean(JA),
            Russian = mean(RU),
            Italian = mean(IT),
            Portuguese = mean(PT),
            Korean = mean(KO)) 
  

l2 <- games_l %>% 
  summarise(English = mean(EN),
            Chinese = mean(ZH),
            German = mean(DE),
            French = mean(FR),
            Spanish = mean(ES),
            Japanese = mean(JA),
            Russian = mean(RU),
            Italian = mean(IT),
            Portuguese = mean(PT),
            Korean = mean(KO))
groups = c("top","all")
groups = data.frame(groups)

l1 <- l1 %>% bind_rows(l2) %>% bind_cols(groups)

l1 <- pivot_longer(l1,cols = English : Korean, names_to = "language",values_to = "value")



l1 %>% filter(language != "English") %>% arrange()%>% ggplot(aes(x = reorder(language, -value), y = value, fill = groups))+
  geom_bar(stat = 'identity',position = 'dodge')+
  scale_y_continuous(name = "Proportion")+
  scale_x_discrete(name = "Languages")+
  scale_fill_manual(values = c("#EFC000FF","#0073C2FF"),name = "",labels = c("All","Top"))+
  theme_classic()+
  theme(legend.position = "top")
```


# Year Updated

### Year updated versus number of ratings in Top 10 % group and All. 
```{r Year updated Versus User rating count (in top 10% by year)}

games_10percpopular <- games %>%
  arrange(desc(user_rating_count))%>%
  filter(user_rating_count > quantile(user_rating_count, .9))


games_10percrate <- games %>%
  arrange(desc(average_user_rating))%>%
  slice(seq(n()*.1))

games_10percpopular$year_updated <- format(games_10percpopular$current_version_release_date, "%Y")

years <- factor(games_10percpopular$year_updated)


ggplot(games_10percpopular, aes(x = years, y = user_rating_count)) +
  scale_y_log10(labels = comma) +
  geom_boxplot(fill = "skyblue") +
  theme_fivethirtyeight() +
  theme(plot.title = element_text(hjust = 0.5, vjust = 2)) +
  labs(title = "Last Updated Apps by Years Among Top 10% User Rating Count")
```

```{r Year updated Versus User rating count (in all by year)}
games$year_updated <- format(games$current_version_release_date, "%Y")

years <- factor(games$year_updated)


ggplot(games, aes(x = years, y = user_rating_count)) +
  scale_y_log10(labels = comma) +
  geom_boxplot(fill = "skyblue") +
  theme_fivethirtyeight() +
  theme(plot.title = element_text(hjust = 0.5, vjust = 2)) +
  labs(title = "Last Updated Apps by Years")

```

# Price and in-app purchases

### Price vs Average User Rating
```{r price vs average user rating}
png(filename="price_aur.png")
games %>%
  filter(price < quantile(games$price, 0.9997)) %>% #Bottom 99.97% of pric dist
  ggplot(aes(average_user_rating, price)) +
    geom_point()+
    geom_jitter()+
    labs(title="Increase in Average User Rating with Increase in Price", 
         x="Average User Rating", y = "Price (USD)")+
    theme_classic()
    
dev.off()
```
used coloring for genre

```{r color for genre}
games %>%
  filter(price < 25) %>%
  ggplot(aes(average_user_rating, price)) +
    geom_point(aes(color = specific_primary_genre))+
    geom_jitter(aes(color = specific_primary_genre))
```

### Price vs total user rating
```{r price vs total user rating}
png(filename="price_tur.png")
games %>%
  filter(price < quantile(games$price, 0.9997),user_rating_count < quantile(games$user_rating_count, 0.9997) ) %>%
  ggplot(aes(price, user_rating_count)) +
    geom_point()+
    geom_jitter()+
    scale_y_continuous(labels = scales::comma)+
    labs(title="Total number of ratings decreases as price increases", 
         x="Price", y = "Total Ratings")+
  theme_classic()
dev.off()
    
```

```{r adding color for avg user rating}
games %>%
  filter(price < 25, user_rating_count > 1000, user_rating_count < 500000) %>%
  ggplot(aes(price, user_rating_count)) +
    geom_point(aes(color = average_user_rating))+
    geom_jitter(aes(color = average_user_rating))+
    scale_color_gradient(low = "red", high = "green")
```

### Price vs avg user rating
```{r added color for tot user count}
games %>%
  filter(price < 25, user_rating_count > 1000, user_rating_count < 500000) %>%
  ggplot(aes(average_user_rating, price)) +
    geom_point(aes(color = user_rating_count))+
    geom_jitter(aes(color = user_rating_count))+
    scale_color_gradient(low = "red", high = "green")
```
### taking top 20% of user rating count

```{r top 20% of data}
games %>%
  top_frac(0.2, user_rating_count) %>%
  select(user_rating_count, everything()) %>%
  arrange(user_rating_count) %>%
  filter(price < 25, user_rating_count < 1000000) %>%
  ggplot(aes(price, user_rating_count)) +
  geom_point(aes(col = average_user_rating))+
  geom_jitter(aes(col = average_user_rating))
```

### Placing price into categories
```{r price categories}
breaks <- c(-Inf, 0.5, 5, 7, 11, Inf)
names <- c("Free", "$1-$3", "$4-$6", "$7-$10", "$10+")
games$price.cat <- cut(games$price, breaks = breaks, labels = names)

games %>%
  top_frac(0.2, user_rating_count) %>%
  ggplot(aes(price.cat)) +
  geom_histogram(stat = "count")
```

```{r new categories}
breaks2 <- c(-Inf, 0.5, 5, Inf)
names2 <- c("Free", "$1-$5", "5+")
games$price.cat2 <- cut(games$price, breaks = breaks2, labels = names2)

games %>%
  top_frac(0.2, user_rating_count) %>%
  ggplot(aes(price.cat2)) +
  geom_histogram(stat = "count")
```

### Top 10 compared to total
```{r in-app purch proportions}
#top 10% of games by user_rating_count
games2 <- games %>%
  top_frac(0.1, user_rating_count)

games3 <- games %>%
  top_frac(-0.9, user_rating_count)

# table that contains dummy variable for in app purchasing
in_app_purch <- table(games2$in_app_purchasing)
in_app_purch


# proportion of games with in app purchasing top 10
in_app_prop <- round(prop.table(in_app_purch),digits=4)
in_app_prop <- data.frame(in_app_prop)

# proportion of games with in app purchasing for whole data set
in_app_purch2 <- table(games$in_app_purchasing)
in_app_purch2


in_app_prop2 <- round(prop.table(in_app_purch2),digits=4)

in_app_prop2 <- data.frame(in_app_prop2)

```

```{r comparing prop for both groups}
#top 10%
in_app_prop_s1 <- in_app_prop[in_app_prop$Var1 == "1" ,]

# total data set
in_app_prop2_s1 <- in_app_prop2[in_app_prop2$Var1 == "1",]

# combining proportion for top 10 and total
combined_prop <- bind_rows(in_app_prop_s1, in_app_prop2_s1)
combined_prop$Group <- ifelse(combined_prop$Freq > 0.65, c("Top"), c("All"))
# plot for in-app proportions
png(filename="inapp_prop_all.png")
ggplot(combined_prop)+
  geom_bar(aes(x = Group, y = Freq, group = Group, fill = Group), stat = 'identity')+
  scale_y_continuous(breaks = c(0, 0.2, 0.4, 0.6, 0.8, 1.0), limits = c(0,1))+
  labs(title= "Proportion of apps with in-app purchases for total market and top 10%",y = "Proportion")+
   scale_fill_manual(values = c("#EFC000FF","#0073C2FF"))+
  theme_classic()
dev.off()
```

```{r price dist}
#pricing distribution
apps_game2 <- apps_game %>%
  filter(price < 10)
ggplot()+
  geom_density(data = games2, aes(x=price), fill = "blue", alpha = 0.2)+
  geom_density(data = apps_game2, aes(x=price), fill = "red", alpha = 0.2)
  
```

```{r combine data for price dist}
#combining top 10 and total data for price
combined_price <- bind_rows(games2, games)
combined_price$Group <- ifelse(combined_price$user_rating_count > 2512, c("Top"), c("All"))
combined_price <- combined_price %>%
  filter(price < quantile(combined_price$price, 0.95))#bottom 95% of price dist

png(filename="price_dist_all.png")
ggplot(combined_price, aes(x = price, fill = Group))+
  geom_density(alpha=0.6)+
  theme_classic()+
  labs(title = "Pricing distribution for total market and top 10%",x="Price", y = "Density")+
  scale_fill_manual(values = c("#EFC000FF","#0073C2FF"))
dev.off()  
```

```{r another price dist}
combined_price <- bind_rows(games2, games)
combined_price$Group <- ifelse(combined_price$user_rating_count > 2512, c("Top"), c("All"))
combined_price95 <- combined_price %>%
  filter(price < quantile(combined_price$price, 0.95)) %>%
  arrange(-price)

png(filename="price_dist2.png")
ggplot(combined_price95, aes(x = price, fill = Group))+
  geom_density(alpha=0.2)+
  theme_classic()+
  labs(x="Price", y = "Density")
dev.off()
```

# Bottom 90 compared to top 10
```{r combine price for top 10 and bot 90}
combined_price2 <- bind_rows(games2, games3)
combined_price2$Group <- ifelse(combined_price2$user_rating_count > 2512, c("Top 10%"), c("Bottom 90%"))
combined_price2 <- combined_price2 %>%
  filter(price < quantile(combined_price$price, 0.95)) %>%
  arrange(-price)

png(filename="price_dist.png")
ggplot(combined_price2, aes(x = price))+
  geom_density(aes(fill = Group), alpha=0.6)+
  theme_classic()+
  labs(title="Pricing distribution for bottom 90% and top 10%", x="Price", y = "Density")+
  scale_fill_manual(values = c("#EFC000FF","#0073C2FF"))
dev.off()
```

```{r in-app purch prop for bot 90}
#Proportion of games with in-app purchases for bottom 90%
in_app_purch3 <- table(games3$in_app_purchasing)
in_app_purch3


in_app_prop3 <- round(prop.table(in_app_purch3),digits=4)

in_app_prop3 <- data.frame(in_app_prop3)

in_app_prop3_s1 <- in_app_prop3[in_app_prop3$Var1 == "1",]

# combining proportion for top 10 and bottom 90
combined_prop2 <- bind_rows(in_app_prop_s1, in_app_prop3_s1)
combined_prop2$Group <- ifelse(combined_prop2$Freq > 0.70, c("Top 10%"), c("Bottom 90%"))

png(filename="inapp_prop.png")
ggplot(combined_prop2)+
  geom_bar(aes(x = Group, y = Freq, group = Group, fill = Group), stat = 'identity')+
  scale_y_continuous(breaks = c(0, 0.2, 0.4, 0.6, 0.8, 1.0), limits = c(0,1))+
  labs(title="Proportion of apps with in-app purchases for bottom 90% and top 10%", y = "Proportion")+
  scale_fill_manual(values = c("#EFC000FF","#0073C2FF"))+
  theme_classic()
dev.off()
```


# Description

Let's check the most frequently used words for top 10% popular games
```{r get the top 10% description of data set}
games_text_top <- games %>% 
  arrange(-user_rating_count) %>% 
  slice(1: (0.1 * nrow(games))) %>% 
  arrange(user_rating_count) %>% select(id, description, price) %>% 
  unnest_tokens(word,description)

```

```{r exclude useless words}
personal_stop_words <- stop_words %>% select(-lexicon) %>% 
  bind_rows(data.frame(word = c("u2022", "u2019s","game","games","http","u0627","app")))
games_text_top <- games_text_top %>% anti_join(personal_stop_words)
```

Free games top 10%
```{r frequently used words for free games in top 10% group}
games_text_top %>% 
  filter(price == 0) %>% 
  count(word, sort = T) %>% slice(1:15) %>% 
  ggplot(aes(x = reorder(word, n, function(n) -n), y = n)) + 
  geom_bar(stat = "identity", fill = "#0073C2FF", alpha = 0.8) + 
  theme_classic() +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
  xlab("Words")+
  scale_y_continuous(name = "count")
  
```

Paid game top10
```{r frequently used words for paid games in top 10% group}
games_text_top %>% 
  filter(price != 0) %>% 
  count(word, sort = T) %>% slice(1:15) %>% 
  ggplot(aes(x = reorder(word, n, function(n) -n), y = n)) + 
  geom_bar(stat = "identity", fill = "#0073C2FF", alpha = 0.8) + 
  theme_classic() +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
  xlab("Words")+
  scale_y_continuous(name = "count")
```


```{r get the text data and exclude useless words}
games_text <- games %>% 
  select(id, description) %>% 
  unnest_tokens(word,description)

personal_stop_words <- stop_words %>% select(-lexicon) %>% 
  bind_rows(data.frame(word = c("u2022", "u2019s","game","games","http","u0627","app")))
games_text <- games_text %>% anti_join(personal_stop_words)
```

All games
```{r frequently used words for all games group}
games_text %>% 
  count(word, sort = T) %>% slice(1:15) %>% 
  ggplot(aes(x = reorder(word, n, function(n) -n), y = n)) + 
  geom_bar(stat = "identity",fill = "#0073C2FF", alpha = 0.8) + 
  theme_classic() +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
  xlab("Words")+
  scale_y_continuous(name = "count")
```

Top 10% games
```{r frequently used words for top 10% group}
games_text_top %>% 
  count(word, sort = T) %>% slice(1:15) %>% 
  ggplot(aes(x = reorder(word, n, function(n) -n), y = n)) + 
  geom_bar(stat = "identity", fill = "#0073C2FF", alpha = 0.8) + 
  theme_classic() +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
  xlab("Words")+
  scale_y_continuous(name = "count")
```

